Wykorzystanie Ethereum do Budowy Zdecentralizowanej Aplikacji

### 2018-06-02 article.tex
Remove samples

\subsubsection{Third Section}
\paragraph{Fourth Level}
Lorem ipsum dolor sit amet, consectetur adipiscing elit.

@@

\newpage
\newpage

\section{Takie tam przydatne przykłady}
\begin{definition} text \end{definition}
\begin{case} text \end{case}
\begin{proof} text \end{proof}

\noindent Widać na równaniu:
\begin{equation}
  x + y = z
\end{equation}

Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
  \includegraphics[width=\textwidth]{fig1.eps}
  \caption{A figure caption is always placed below the illustration.
    Please note that short captions are centered, while long ones are
  justified by the macro package automatically.} \label{fig1}
\end{figure}

Tabla~\ref{tab1} przedstawia że działa.

\begin{table}
  \caption{Table captions should be placed above the
  tables.}\label{tab1}
  \begin{tabular}{|l|l|l|}
    \hline
    Heading level &  Example & Font size and style\\
    \hline
    Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
    1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
    2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
    3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
    4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
    \hline
  \end{tabular}
\end{table}

% ########## END OF SAMPLES

>>>>

@@

% \newpage
% \newpage

% \section{Takie tam przydatne przykłady}
% \begin{definition} text \end{definition}
% \begin{case} text \end{case}
% \begin{proof} text \end{proof}

% \noindent Widać na równaniu:
% \begin{equation}
%   x + y = z
% \end{equation}

% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).

% \begin{figure}
%   \includegraphics[width=\textwidth]{fig1.eps}
%   \caption{A figure caption is always placed below the illustration.
%     Please note that short captions are centered, while long ones are
%   justified by the macro package automatically.} \label{fig1}
% \end{figure}

% Tabla~\ref{tab1} przedstawia że działa.

% \begin{table}
%   \caption{Table captions should be placed above the
%   tables.}\label{tab1}
%   \begin{tabular}{|l|l|l|}
%     \hline
%     Heading level &  Example & Font size and style\\
%     \hline
%     Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
%     1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
%     2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
%     3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
%     4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
%     \hline
%   \end{tabular}
% \end{table}

% % ########## END OF SAMPLES
